\begin{frame}{References \& Further Reading}
  \footnotesize
  \begin{thebibliography}{9}
    \bibitem{shirley}
    Peter Shirley and Steve Marschner et~al.
    \textit{Fundamentals of Computer Graphics (4th Edition)}.
    CRC Press, 2016.\\
    \href{http://repo.darmajaya.ac.id/5422/}{Available as PDF}

    \bibitem{pharr4}
    Matt Pharr, Wenzel Jakob, and Greg Humphreys.
    \textit{Physically Based Rendering: From Theory to Implementation (4th Edition)}.
    Morgan Kaufmann, 2023.\\
    \href{https://pbr-book.org/4ed/contents}{Available online}

    \bibitem{phong}
    Bui Tuong Phong.
    \textit{Illumination for Computer Generated Pictures}.
    Communications of the ACM, 18(6):311-317, 1975.

    \bibitem{blinn}
    James F. Blinn.
    \textit{Models of light reflection for computer synthesized pictures}.
    ACM SIGGRAPH Computer Graphics, 11(2):192-198, 1977.

    \bibitem{kajiya}
    James T. Kajiya.
    \textit{The Rendering Equation}.
    ACM SIGGRAPH Computer Graphics, 20(4):143-150, 1986.

    \bibitem{realtime}
    Tomas Akenine-Möller, Eric Haines, and Naty Hoffman.
    \textit{Real-Time Rendering (4th Edition)}.
    CRC Press, 2018.

    \bibitem{learnopengl}
    Joey de Vries.
    \textit{Learn OpenGL - Lighting}.\\
    \href{https://learnopengl.com/Lighting/Basic-Lighting}{learnopengl.com/Lighting}

    \bibitem{scratchapixel}
    Scratchapixel: Introduction to Shading.\\
    \href{https://www.scratchapixel.com/lessons/3d-basic-rendering/introduction-to-shading}{scratchapixel.com/shading}
  \end{thebibliography>
  \end{frame}
